Human capital mediates natural selection in contemporary humans

### 2022-01-02 why-natural-selection.Rmd
bugfixes

\FloatBarrier
\clearpage
## Parents' generation {#sec-parents}

@@

\clearpage
\FloatBarrier
## Parents: area deprivation

@@

\clearpage
\FloatBarrier
## Parents: age at first live birth

@@

famhist_bo1 <- famhist %>% 
                 filter(birth_order == 1) %>%
                 select(n_siblings, whr_combined, moth_age_flb_cat, 
                          fath_age_flb_cat)

@@

res_age_flb_mothers_cross %>% 
      mutate(
        `Age at first live birth` = gsub("moth_age_birth_cat(.*):.*", "\\1", term),
        `Age at first live birth` = add_n(`Age at first live birth`, 
                                          "moth_age_flb_cat", dv = "n_sibs",
                                          data = famhist_bo1)
      ) %>% 
      standard_ggplot(score_col = score_name, 
                      fill_col = `Age at first live birth`, n_regs = n_regs,
                      fill_direction = -1)

@@

res_age_flb_fathers_cross %>% 
      mutate(
        `Age at first live birth` = gsub("fath_age_birth_cat(.*):.*", "\\1", term),
        `Age at first live birth` = add_n(`Age at first live birth`, 
                                          "fath_age_flb_cat", dv = "n_sibs",
                                          data = famhist_bo1)
      ) %>% 
      standard_ggplot(score_col = score_name, 
                      fill_col = `Age at first live birth`, n_regs = n_regs,
                      fill_direction = -1)

@@

```{r plot-res-fe-fertility, fig.cap = "Selection effects controlling for sibling-group fixed effects, with and without a control for education (left education before 16, 16-18, or after 18). Each set of results is from a single regression of 'n children' on 29 polygenic scores. Standard errors clustered by sibling group."}

>>>>

\FloatBarrier
\clearpage
## Parents' generation {#sec-parents}
### Selection effects

@@

\clearpage
\FloatBarrier
### Area deprivation

@@

\clearpage
\FloatBarrier
### Age at first live birth

@@

famhist_bo1 <- famhist %>% 
                 filter(birth_order == 1) %>%
                 select(n_sibs, whr_combined, moth_age_birth_cat, 
                          fath_age_birth_cat)

@@

res_age_flb_mothers_cross %>% 
      mutate(
        `Age at first live birth` = gsub("moth_age_birth_cat(.*):.*", "\\1", term),
        `Age at first live birth` = add_n(`Age at first live birth`, 
                                          "moth_age_birth_cat", dv = "n_sibs",
                                          data = famhist_bo1)
      ) %>% 
      standard_ggplot(score_col = score_name, 
                      fill_col = `Age at first live birth`, n_regs = n_regs,
                      fill_direction = -1)

@@

res_age_flb_fathers_cross %>% 
      mutate(
        `Age at first live birth` = gsub("fath_age_birth_cat(.*):.*", "\\1", term),
        `Age at first live birth` = add_n(`Age at first live birth`, 
                                          "fath_age_birth_cat", dv = "n_sibs",
                                          data = famhist_bo1)
      ) %>% 
      standard_ggplot(score_col = score_name, 
                      fill_col = `Age at first live birth`, n_regs = n_regs,
                      fill_direction = -1)

@@

```{r plot-res-fe-fertility, fig.cap = "Selection effects controlling for sibling-group fixed effects, with and without a control for education (left education before 16, 16-18, or after 18). Each set of results is from a single regression of \\emph{n children} on 29 polygenic scores. Standard errors clustered by sibling group."}
